Solutions to Integer Programming from Quantum Annealing

### 2020-09-11 paper/main.tex

In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown in Fig.~\ref{fig:anneal_schedule_ext}. With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians. The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.

@@

>>>>

@@

In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}. With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians. The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.

The quantum system can be further idealized by including only the full-counting statistics model (blue), or local decoherence (green). We observe in both cases that the overall scaling follows the story of the MBL hypothesis. Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of $|h_i|$, exhibits the same scaling as experiment. This result suggests that our strategy for setting annealing offsets is improving the algorithm beyond the simple explanation of qubits freezing due to single-particle amplitude damping. In fact, the simulation with only amplitude damping (green) does not fully capture the results of the experiment. We observe hints of a phase transition with respect to offset (which may be thought of as some measure of disorder) when dynamical thermalization effects are removed. This is a tantalizing observation, and also is strong evidence for the inclusion of the full-counting statistics model.

It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to 1 within machine precision.
